Cover letter for the original IJRR submission

### 2017-05-09 body/conclusion.tex
final version

As demonstrated in the results section, the main interest of our method is time performance. Time performance is critical for 
online applications with the robot, a goal not satisfied by any of the previous contributions. Our method addresses highly constrained environments while improving the search time by orders of magnitude. This high performance is reached at the cost of some approximations that we discuss here. 
%~ In previous approaches, we identified 2 sources of high computational cost.

>>>>

As demonstrated in the results section, the main interest of our method is the reduction of the algorithmic complexity of the problem, which leads to an interactive 
application. This property is critical for 
online applications with the robot and was not proposed by any of the previous contributions. Our method addresses highly constrained environments while improving the search time by orders of magnitude. This high performance is reached at the cost of some approximations that we discuss here. 
%~ In previous approaches, we identified 2 sources of high computational cost.

### 2017-05-09 body/overview.tex
final version

Figure~\ref{fig:framework} illustrates our work flow.
\Pa and \Pb are addressed sequentially: From a given problem (a) we first plan a root guide path (b), before
extending it into a sequence of static equilibrium configurations(c). In the case where step c fails,
our framework invalidates the computed guide path, and restarts the planning from b.

>>>>

Figure~\ref{fig:framework} illustrates our work flow.
\Pa and \Pb are addressed sequentially: From a given problem (a) we first plan a root guide path (b), before
extending it into a sequence of static equilibrium configurations (c). In the case where step (c) fails,
our framework invalidates the computed guide path, and restarts the planning from (b).
